\documentclass{article}

\usepackage{tikz-cd, amsmath, amssymb, amsthm, mathtools}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern} % Better standard font

\begin{document}

\section{Polynomial Functors}

Give semantics to W-Types, which should be enough for our case (hopefully). By encoding a set of operations an their arities, which we can think of as the type constructors. Where B are the operations and A the arities, we each also fibre them over a set of types. We only consider endofunctors here.

\begin{center}
    \begin{tikzcd}
        & A \ar[r] \ar[dl] & B \ar[dr] & \\
        I & & & I
    \end{tikzcd}
\end{center}

\section{Given Constructors}

We need the subtype to be stable under these, so we need an $F-Alg$ for the polynomial functor build from the constructors.

\begin{center}
    \begin{tikzcd}
        F(\Sigma_{x:X} P(x)) \ar[d, "\alpha"] \\
        \Sigma_{x:X} P(x)
    \end{tikzcd}
\end{center}

Therefore, we need something like $F(P)(F(x)) \implies P(x)$, from now on called a predicate being stable under $F$. Further if $P$ is the smallest such predicate, so for all predicates $Q$ stable under $F$ we have $P(x) \implies Q(x)$ we can then $\Sigma_{x:X} P(x)$ should be initial under the $\Sigma$ types, by just applying $F$ to the obvious function. Why this is unique needs some work still.

\begin{center}
    \begin{tikzcd}
        F(\Sigma_{x:X} P(x)) \ar[d, "\alpha"] \ar[r, "F(f)"] & F(\Sigma_{x:X} Q(x)) \ar[d, "\delta"]\\
        \Sigma_{x:X} P(x) \ar[r, "f"] & \Sigma_{x:X} Q(x)
    \end{tikzcd}
\end{center}

Finally, by building a prediacte which should be something like $\forall a:A \exists a' : A\ \ s.t. \ \ a = \tau(F(a'))$ we where $F(A) \rightarrow_{\tau} A$ is some F algebra. We should be able to build a subtype with an $F$-stable predicate that is isomorphic to $A$ and therefore get initiality for all algebras.

\end{document}